Rice yield improvements by plant breeding are offset by decreases over time

### 2017-05-04 output/breed_paper.Rnw
Cleaned up unused code

invisible(sapply(1:2, function(i){
    plot(mean ~ year,
         data = plot_data[[i]],
         xlim = c(1995, 2016), ylim = c(7500,13500),
         pch = 16, main = gsub("M","M-", tars[i]),
         ylab = "",
         yaxt = "n",
         xlab = "Years after release")
    segments(x0 = plot_data[[i]]$year,
             y0 = plot_data[[i]]$mean + plot_data[[i]]$se,
             y1 = plot_data[[i]]$mean - plot_data[[i]]$se)
    if(i == 1){
        axis(2)
        mtext(expression("Yield ( kg ha"^-1~")"), 2, line = 2.25, cex.lab = 0.6)
    }
#     abline(lm(yield_kg*1.12 ~ year,
    #               data = mod_data[(mod_data$id == tars[i] & mod_data$site == "RES"),]),
    # lty = 2)

@@

# invisible(sapply(tars, function(x){
#     plot(yield_kg  ~ year,
#          data = mod_data[(mod_data$id == x & mod_data$site == "RES"),],
#          xlim = c(1995, 2016), ylim = c(6500,14500),
#          pch = 16,
#          col = rgb(0,0,0,0.5),
#          main = gsub("M", "M-", x),
#          ylab = "",
#          yaxt = "n",
#          xlab = "Year")
#     if(x == "M202"){
#         axis(2)
#         mtext(expression("Yield ( kg ha"^-1~")"), 2, line = 2.25, cex.lab = 0.6)
#     }
#     # abline(lm(yield_kg ~ year, data = mod_data[(mod_data$id == x & mod_data$site == "RES"),]), lty = 2)
#     abline(h = mean(mod_data$yield_kg[(mod_data$id == x & mod_data$site == "RES")] ),
#            lty = 2)
# }))

@@

% \begin{figure}[h]

% <<fig=TRUE, echo=FALSE>>=
% yrs_in <- -6:34
% pp <- posterior_predict(RES_yrs_fit, re.form = NA, newdata = data.frame(yrs_in_trial = yrs_in))
% pp <-  (pp * scl + center)

% ints <- apply(pp, 2, quantile, p = c(0.05, 0.5, 0.95))

% plot_data = as.data.frame(tapply(mod_data$yield_kg , mod_data$yrs_in_trial, mean))
% plot_data$se = tapply(mod_data$yield_kg , mod_data$yrs_in_trial, function(x)
%     sd(x)/sqrt(length(x)))
% plot_data$tmp = as.numeric(row.names(plot_data))
% colnames(plot_data) = c("yield_kg", "yield_se", "yrs_in_trial")

% plot(yield_kg ~ yrs_in_trial, data = plot_data, pch = 16, #col = rgb(0,0,0,0.25),
%      xlab = "Year since entry",
%      ylab = expression("Yield ( kg ha"^-1~")"),
%      ylim = c(8700, 11200))
% with(plot_data, segments(x0 = yrs_in_trial, y0=yield_kg + yield_se,
%                          y1 = yield_kg - yield_se))
% abline(a = ((fixef(RES_yrs_fit)[1] * scl) + center) , b = fixef(RES_yrs_fit)[2] * scl)
% # lines(x = yrs_in, y = ints[2,], lty = 2) 
% # polygon(x = c(yrs_in, rev(yrs_in)), y = c(ints[1,],rev(ints[3,])), col = rgb(0,0,0,0.2), border = NA)
% text(30, 4500, bquote(.(round(fixef(RES_yrs_fit)[2] * scl, 1))~lbs~year^-1))

% @ 
% \caption{There is a small decrease in yield over the time since a
  % cultivar was entered into the trial using the full data
  % set. However, the effect is small (\Sexpr{round(fixef(RES_yrs_fit)[2] * scl, 1)}
  % lbs year\textsuperscript{-1}) in relation to the variability
  % between sites and years.}
% \label{fig:yrs}
% \end{figure}

@@

<<fig=TRUE, echo=FALSE, width = 6, height = 5>>=
# par(mfrow = c(1, length(tars)),
#     mar = c(4,0,2,0),
#     oma = c(4,4,0.5,0.5))

@@

# invisible(sapply(1:2, function(i){
#     plot(mean ~ yrs_in_trial,
#          data = plot_data[[i]],
#          xlim = c(-6, 36), ylim = c(6500,14500),
#          pch = 16, main = gsub("M","M-", tars[i]),
#          ylab = "",
#          yaxt = "n",
#          xlab = "Years after release")
#     segments(x0 = plot_data[[i]]$yrs_in_trial,
#              y0 = plot_data[[i]]$mean + plot_data[[i]]$se,
#              y1 = plot_data[[i]]$mean - plot_data[[i]]$se)
#     if(i == 1){
#         axis(2)
#         mtext(expression("Yield ( kg ha"^-1~")"), 2, line = 2.25, cex.lab = 0.6)
#     }
#     abline(lm(yield_kg*1.12 ~ yrs_in_trial,
#               data = mod_data[(mod_data$id == tars[i] & mod_data$site == "RES"),]),
#            lty = 1, col = "grey50")
# }))

@@

% \begin{figure}[h]

% <<fig=TRUE, echo=FALSE>>=
% yrs <- 1980:2015
% pp <- posterior_predict(RES_rel_fit, re.form = NA,
%                         newdata = data.frame(release_yr_c = yrs - 2000))
% pp <-  pp * scl + center

% ints <- apply(pp, 2, quantile, p = c(0.05, 0.5, 0.95))

% plot(yield_kg ~ release_yr, data = mod_data[RES,], pch = 16, col = rgb(0,0,0,0.25),
%      xlab = "Year of Release",
%      ylab =  expression("Yield ( lbs acre"^-1~")"))
% lines(x = yrs, y = ints[2,], lty = 2) 
% polygon(x = c(yrs, rev(yrs)), y = c(ints[1,],rev(ints[3,])), col = rgb(0,0,0,0.2), border = NA)
% text(2010, 4500, bquote(.(round(fixef(RES_rel_fit)[2] * scl, 1))~lbs~year^-1))
% @

% \caption{The effect of year of release on yield for only data from the
%   Rice Experiment Station (RES). There is an estimated
%   increase in yield over time, but it is smaller than the previously estimated 54 lbs
%   year\textsuperscript{-1}}
% \label{fig:RES_release}
% \end{figure}

>>>>

invisible(sapply(1:2, function(i){
    plot(mean ~ year,
         data = plot_data[[i]],
         xlim = c(1995, 2016), ylim = c(7500,13500),
         pch = 16, main = gsub("M","M-", tars[i]),
         ylab = "",
         yaxt = "n",
         xlab = "Years after release")
    segments(x0 = plot_data[[i]]$year,
             y0 = plot_data[[i]]$mean + plot_data[[i]]$se,
             y1 = plot_data[[i]]$mean - plot_data[[i]]$se)
    if(i == 1){
        axis(2)
        mtext(expression("Yield ( kg ha"^-1~")"), 2, line = 2.25, cex.lab = 0.6)
    }

@@

@@

@@

<<fig=TRUE, echo=FALSE, width = 6, height = 5>>=

@@

@@
